---
title: 'Statistics: Linear Regression'
author: "Scott Schumacker"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This project will show an example linear regression analysis using the cars data set. We will be analyzing the linear relationship between the distance to stop variable and the speed variable.

***Loading Packages***
```{r}
library(tidyverse)
library(lmtest)
```

## Creating a data set
For this example linear regression analysis, we will be using the cars data. Preview of the data:
```{r}
head(cars)
```

After seeing a preview of the data set, we can visualize the relationship between these two variables to see if there may be a linear relationship.

***Visualizing linear relationship***
```{r}
# Visualizing data as scatter plot
cars %>% 
  ggplot(aes(speed, dist)) +
  geom_point() +
  theme_classic()
```

There appears to be a positive correlation between speed and distance. We can create a linear model to further examine any linear relationship.

Before creating our linear model we can create our Hypothesis: <br>
H0: The slope of the regression equals 0 (B0 = 0) <br>
Ha: The slope of the regression does not equal 0 (B0 != 0)

We can use an alpha of 0.05.

***Creating linear model***
```{r}
# Creating model summary
cars %>% 
  lm(dist ~ speed, data = .) %>% 
  summary()
```
### Results
The model output shows us that there is a significant linear relationship between speed and distance and that we can reject our null hypothesis (p-value = 1.49e-12). In addition, from the R-squared value, we can see that speed explains 65% of the variation in distance.

***Visualizing linear trend***

We can re-create the data visualization with a linear trend line drawn on top:
```{r}
# Visualizing data with linear trend line added
cars %>% 
  ggplot(aes(speed, dist)) +
  geom_point() +
  geom_smooth(method = "lm", se = F) +
  theme_classic()
```

***Checking linear regression assumptions***

To make sure that the linear regression analysis is valid, we also need to check the assumptions.

We can first check for normality of the model residuals:
```{r}
lmModel <- lm(dist ~ speed, data = cars)

# Checking normality of residuals
hist(lmModel$residuals)
```

We can see that the residuals show a normal distribution and are centered around 0.

In addition, we can check for homoscedasticity of variance of the residuals using the Breusch-Pagan Test with an alpha of 0.05:
```{r}
bptest(lmModel)
```
Since our p-value is greater than our alpha of 0.05, we can assume equal variance in the model residual.