---
title: 'Statistics: Linear Regression'
author: "Scott Schumacker"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This project will show an example linear regression analysis using the cars data set. We will be analyzing the linear relationship between the distance to stop variable and the speed variable.

***Loading Packages***
```{r}
library(tidyverse)
library(lmtest)
```

## Creating a data set
For this example linear regression analysis, we will be using the cars data. Preview of the data:
```{r}
head(cars)
```

After seeing a preview of the data set, we can visualize the relationship between these two variables to see if there may be a linear relationship.

***Visualizing linear relationship***
```{r}
# Visualizing data as scatter plot
cars %>% 
  ggplot(aes(speed, dist)) +
  geom_point() +
  theme_classic()
```

There appears to be a positive correlation between speed and distance. We can create a linear model to further examine any linear relationship.

```{r}
# Creating model summary
cars %>% 
  lm(dist ~ speed, data = .) %>% 
  summary()
```
The model output shows us that there is a significant linear relationship between speed and distance (p-value = 1.49e-12) and that speed explains 65% of the variation in distance.